%-------------------------
% Resume in Latex
% Author : David Ashworth
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large David Ashworth}} & \href{mailto:dca.account@gmail.com}{dca.account@gmail.com}\\
  & +1-682-225-4590 \\
  & github: \href{https://github.com/daveashworth}{@daveashworth}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Baylor University}{Waco, TX}
      {Master of Science in Computer Science;  GPA: 3.53}{Aug. 2002 -- May. 2004}
    \resumeSubheading
      {Baylor University}{Waco, TX}
      {Bachelor of Science in Computer Science;  GPA: 3.67}{Aug. 1998 -- May. 2002}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {HigherEducation.com}{Remote/Houston, TX}
      {Full Stack Software Engineer}{Mar 2016 - Present}
      \resumeItemListStart
        \resumeItem
          {Create and maintain widgets in a scalable and efficient platform used for serving monetization products to schools and affiliate partners. Involved in building out the GraphQL API, several of the monetization widgets and related dynamic documentation.}
        \resumeItem
          {Built new widgets used for serving linkouts to prospective students. Involved from the inception to development of the system and associated tracking of the student until conversion with a school.}
        \resumeItem
          {Build all these full stack apps using lots of fun technologies (Node, React, Express, ES6/ES7, GraphQL, MobX, Knex, MySQL, PostgreSQL, and more...)}
      \resumeItemListEnd


    \resumeSubheading
      {Apex Capital Corp}{Fort Worth, TX}
      {Senior Software Engineer}{Sep 2010 - Mar 2016}
      \resumeItemListStart
        \resumeItem
          {Collaborated with a small team of software engineers and product owners to design, develop, and maintain a host of internal and external facing web applications.}
        \resumeItem
          {Worked with a team of three developers to design and develop a free load board for truckers using Angular and Java. Envisioned and created a unique caching solution using memcached to drastically improve the load matching performance of the system.}
        \resumeItem
          {Worked with one other developer using new technology (to me) to convert our load board's load search/matching functionality from Java/Oracle to Node, Express, SocketIO, and MongoDB in one day.}
        \resumeItem
          {Played a key role in designing the UX and functionality of our iOS and Android apps. Sole developer of the over 40 RESTful web services used by our iOS and Android mobile apps to facilitate clients managing invoices and their associated images.}
      \resumeItemListEnd

    \resumeSubheading
      {Raytheon}{Alice Springs, Australia}
      {Software Engineer}{Dec 2004 - Sept 2010}
      \resumeItemListStart
        \resumeItem
          {Worked with a small team of developers to build and maintain distributed intranet applications used locally and across the world by multiple corporations and government agencies.}
        \resumeItem
          {Developed a data exchange network and cross-site web applications to share system engineering data and documentation to facilitate better collaboration and support between our local and remote engineering sites.}
        \resumeItem
          {Supported and maintained the hardware and software of these systems for a government mandated 24/7/365 up-time.}
      \resumeItemListEnd

%    \resumeSubheading
%      {Baylor University}{Waco, TX}
%      {Grad School Assistant}{Aug 2002 - Dec 2003}
%      \resumeItemListStart
%        \resumeItem
%          {Taught Pre/AP Computer Science classes at a local high school through an arrangement with the university. %Involved in creating the lessons, homework, projects, teaching, assessing and after school tutoring of students in %preparation for students taking the AP Computer Science test.}
%      \resumeItemListEnd%
%
  \resumeSubHeadingListEnd


%-----------Additional Skills-----------------
\section{Additional Skills}
  \resumeSubHeadingListStart
    \resumeItem
      {Team player willing to do whatever it takes to help my organization succeed.}
    \resumeItem
      {Strong development and testing skills including experience with several technologies including Node, Express, GraphQL, React, Angular, HTML, CSS, Java, Git, and SQL.}
    \resumeItem
      {Driven learner who can come up to speed on new technologies quickly.}
    \resumeItem
      {Experienced with the full lifecycle of software development and moving solutions daily from staging through to production using peer code reviews, CI, and automated testing.}
    \resumeItem
      {More than 15 years experience developing applications for the web.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

