%-------------------------
% Resume in Latex
% Author : David Ashworth
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

  \usepackage{latexsym}
  \usepackage[empty]{fullpage}
  \usepackage{titlesec}
  \usepackage{marvosym}
  \usepackage[usenames,dvipsnames]{color}
  \usepackage{verbatim}
  \usepackage{enumitem}
  \usepackage[pdftex]{hyperref}
  \usepackage{fancyhdr}


  \pagestyle{fancy}
  \fancyhf{} % clear all header and footer fields
  \fancyfoot{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}

  % Adjust margins
  \addtolength{\oddsidemargin}{-0.375in}
  \addtolength{\evensidemargin}{-0.375in}
  \addtolength{\textwidth}{1in}
  \addtolength{\topmargin}{-.5in}
  \addtolength{\textheight}{1.0in}

  \urlstyle{same}

  \raggedbottom
  \raggedright
  \setlength{\tabcolsep}{0in}

  % Sections formatting
  \titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

  %-------------------------
  % Custom commands
  \newcommand{\resumeItem}[1]{
    \item\small{
      {#1 \vspace{-2pt}}
    }
  }

  \newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
      \end{tabular*}\vspace{-5pt}
  }

  \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

  \renewcommand{\labelitemii}{$\circ$}

  \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
  \newcommand{\resumeItemListStart}{\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

  %-------------------------------------------
  %%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


  \begin{document}

  %----------HEADING-----------------
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{{\Large Dave Ashworth}} & +1-682-225-4590 \\
    & \href{mailto:dave@daveashworth.com}{dave@daveashworth.com}\\
    & \href{https://github.com/daveashworth}{GitHub: @daveashworth}\\
    & \href{https://www.linkedin.com/in/daveashworth/}{Linkedin: daveashworth}
  \end{tabular*}

  %-----------SUMMARY-------------------
  \section{Summary}
  Software engineer with over 20 years of experience delivering impactful software solutions. Skilled in full-stack development and adept at learning and implementing new technologies. Strong believer in the value of effective communication and collaboration for successful product development and positive teamwork. Seeking an opportunity to make a meaningful impact through my work.

  %-----------EXPERIENCE-----------------
  \section{Experience}
    \resumeSubHeadingListStart

    \resumeSubheading
        {Uplifting Medi Spa - Family Business}{Remote/New Braunfels, TX}
        {Lead Software Engineer}{May 2023 - Current}
        \resumeItemListStart
            \resumeItem
                {Designed and implemented a customer database, automating the import of customer data and rewards points integration with Alle/Allergan. Developed an SMS notification system alerting customers of expiring rewards with booking links, improving engagement. Used Planetscale, Prisma, node.js, AWS lambdas, resend, twilio, turborepo.}
            \resumeItem
                {Initiated development of a React Native EHR app for providers documenting procedures (e.g., Botox, fillers) but paused the project due to funding limitations.}
            \resumeItem
                {Built a telehealth scheduling solution using Doximity, enabling customers to book, pay for, and attend virtual weight loss counseling sessions.}
            \resumeItem
                {Launched and managed a Shopify store for skincare products, overseeing ongoing updates and improvements to the store’s design and functionality.}
        \resumeItemListEnd

    \resumeSubheading
        {Apex Capital Corp}{Remote/Fort Worth, TX}
        {Senior Software Engineer}{July 2020 - May 2023}
        \resumeItemListStart
          \resumeItem
            {Designed and developed a high-performance payments platform enabling clients and partners to self-manage capital reserves with improved user experience and efficiency. Used Next.js, tailwindcss.}
        \resumeItemListEnd

      \resumeSubheading
        {HigherEducation.com (acquired by Red Ventures)}{Remote/Houston, TX}
        {Full Stack Software Engineer}{Mar 2016 - July 2020}
        \resumeItemListStart
          \resumeItem
            {Overhauled the core ad server's decision engine, processing over a million requests daily, reducing response times by 50\%, and increasing revenue by \$200k by optimizing traffic capture without caching dependencies.}
          \resumeItem
            {Spearheaded development of the decision engine, optimizing ad rankings and driving a 10\% revenue boost by enhancing the precision of ad placements.}
          \resumeItem
            {Developed lightweight, embeddable UI components served to millions of users monthly, leveraging a centralized GraphQL API to ensure high performance and scalability.}
          \resumeItem
            {Built an inventory management system integrating disparate spreadsheets via a centralized API, reducing manual errors and saving employees several hours of work weekly.}
        \resumeItemListEnd

      \resumeSubheading
        {Apex Capital Corp}{Fort Worth, TX}
        {Senior Software Engineer}{Sep 2010 - Mar 2016}
        \resumeItemListStart
          \resumeItem
            {Designed and developed a scalable load board for truckers, hosting millions of loads and providing real-time load matching for users. Used Angular, node.js, Java, and SQL.}
          \resumeItem
            {Created a unique caching solution using memcached that reduced load matching times from 10 seconds to near-instantaneous, significantly enhancing the platform's user experience.}
          \resumeItem
            {Led the redesign of the mobile app’s UX and architected over 40 RESTful web services, resulting in reduced client churn and a substantial increase in new client acquisitions. Used Java.}
        \resumeItemListEnd

      \resumeSubheading
        {Raytheon}{Alice Springs, Australia}
        {Software Engineer}{Dec 2004 - Sept 2010}
        \resumeItemListStart
          \resumeItem
            {Collaborated with a team to design and maintain distributed intranet applications, used globally by corporations and government agencies, ensuring reliable, secure communication across international networks. Used Java, Struts.}
          %\resumeItem
          %  {Engineered a configuration management system used by on-site engineers to prep for hardware installations which directly contributed to less time spent on site by TDY install teams and reduced costs to the government.}
        \resumeItemListEnd

  %    \resumeSubheading
  %      {Baylor University}{Waco, TX}
  %      {Grad School Assistant}{Aug 2002 - Dec 2003}
  %      \resumeItemListStart
  %        \resumeItem
  %          {Taught Pre/AP Computer Science classes at a local high school through an arrangement with the university. %Involved in creating the lessons, homework, projects, teaching, assessing and after school tutoring of students in %preparation for students taking the AP Computer Science test.}
  %      \resumeItemListEnd%
  %
    \resumeSubHeadingListEnd

    %-----------EDUCATION-----------------
  \section{Education}
      \resumeSubheading
        {Baylor University}{M.S. and B.S in Computer Science}

  %
  %--------PROGRAMMING SKILLS------------
  %\section{Programming Skills}
  %  \resumeSubHeadingListStart
  %    \item{
  %      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
  %      \hfill
  %      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
  %    }
  %  \resumeSubHeadingListEnd


  %-------------------------------------------
  \end{document}

